Nic Steyn

### 2025-08-04 site/papers.qmd
paper update

@@

**Steyn, N.**, & Parag, K. V. (2025). Robust uncertainty quantification in popular estimators of the instantaneous reproduction number. *Accepted at American Journal of Epidemiology*. Preprint accessible here: [https://doi.org/10.1101/2024.10.22.24315918](https://doi.org/10.1101/2024.10.22.24315918)

@@

>>>>

# Recent publications

**Steyn, N.**, & Parag, K. V. (2025). Robust uncertainty quantification in popular estimators of the instantaneous reproduction number. *American Journal of Epidemiology*. [https://doi.org/10.1093/aje/kwaf165](https://doi.org/10.1093/aje/kwaf165)

*A complete list of publications can be found lower on this page.*

@@

@@

**Steyn, N.**, & Parag, K. V. (2025). Robust uncertainty quantification in popular estimators of the instantaneous reproduction number. *American Journal of Epidemiology*. [https://doi.org/10.1093/aje/kwaf165](https://doi.org/10.1093/aje/kwaf165)
